%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}


\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.2in}
% \addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSlimSubheading}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\setlength{\footskip}{4.08003pt}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
	\textbf{\href{https://www.filippovisconti.com}{\Large Filippo Visconti}}\\
	\href{https://www.filippovisconti.com}{\underline{filippovisconti.com}}  & \href{mailto:filippo@filippovisconti.com}{\underline{filippo@filippovisconti.com}}\\
	\href{https://www.linkedin.com/in/filippo-visconti/}{\underline{linkedin.com/in/filippo-visconti}} &  +39 346 491 5591
\end{tabular*}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Eidgenössische Technische Hochschule Zürich}{Zürich (Switzerland)}
{Master of Science in Computer Science}{Sept. 2022 -- exp. Aug. 2024}
\resumeItemListStart
\resumeItem{Major in \textbf{Secure and Reliable Systems} - Minor in \textbf{Networking}}
\resumeItem{Current GPA: $5.35$/$6.0$.}
\resumeItem{Final thesis: \textsl{"Securing satellite receiver firmware upgrades"} in collaboration with \emph{armasuisse}}
\resumeItem{Thesis supervisors: Prof. Shweta Shinde and Dr. Vincent Lenders}

\resumeItemListEnd

\resumeSubheading
{Università degli Studi Roma TRE}{Rome (Italy)}
{Bachelor of Science in Computer Engineering}{Sept. 2019 -- July 2022}
\resumeItemListStart
\resumeItem{Graduated with 110/110 cum Laude}
\resumeItem{Final GPA: $28.9$/$30.0$.}
\resumeItem{Final thesis: \textsl{"Realization of a cyber defense system: analysis of VPN solutions."}}
\resumeItem{Thesis supervisor: Prof.~Maurizio Patrignani}

\resumeItemListEnd

\resumeSubheading
{Pugwash District High School}{Pugwash (Canada) }
{Canadian High School Diploma }{Sept. 2017 -- Jun. 2018}
\resumeItemListStart
\resumeItem{Graduated with Honors.}
\resumeItem{Final GPA: $98$/$100$.}
\resumeItemListEnd

\resumeSubheading
{Liceo Scientifico Statale Farnesina}{Rome (Italy)}
{Italian High-School Diploma in Scientific Studies}{Sept. 2014  -- July 2019}
\resumeItemListStart
\resumeItem{Final Mark: $92$/$100$.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Technical Skills}
\resumeSubHeadingListStart
\resumeSlimSubheading
{Tools and Libraries}{}
\resumeItemListStart
\resumeItem{Virtualization: Docker, LXC, VMware, VirtualBox, Proxmox VE, ESXi,  }
\resumeItem{Network: WireGuard, OpenVPN, Wireshark, nmap, iptables, Squid, Snort}
\resumeItem{Linux services: Ansible, PostgreSQL, MySQL, Apache, Nginx, Samba, Bind, Dnsmasq, DHCPd}
\resumeItem{Databases: MySQL, PostgreSQL, SQLite}
\resumeItem{Binary analysis: Ghidra, GDB, Valgrind, AFL}
\resumeItem{Web: Flask, Springboot, React, Next.JS}
\resumeItem{High Performance Computing: OpenMP, MPI, basics of CUDA, SIMD instructions, Intel Intrinsics}
\resumeItem{Misc: Git, GitHub Actions, LaTeX, Vim, Makefile}

\resumeItemListEnd

\resumeSlimSubheading
{Programming Languages}{}
\resumeItemListStart
\resumeItem{C: POSIX syscalls, threads and processes management, parallel programming, }
\resumeItem{Java, C$\sharp$, Python}
\resumeItem{Bash and basics of: OCaml, Go, TypeScript, PHP}
\resumeItemListEnd

\resumeSubheading
{Projects}{}
{Full portfolio on \href{https://github.com/filippovisconti}{\underline{GitHub}} }{}
\resumeItemListStart
\resumeItem{2024 -- \href{https://github.com/filippovisconti/barber-shop}{\underline{Barber Shop}} -- Developed a web app for a fictitious barber shop using Next.JS with a booking system.}
\resumeItem{2023 -- \href{https://github.com/filippovisconti/dphpc-project}{\underline{Blake}} -- Developed a multi-threaded, optimized version of the Blake algorithm in C.}
\resumeItem{2023 -- Rowhammer -- Implemented a Rowhammer attack in C.}
\resumeItem{2023 -- Worst Case Optimal Joins -- Implemented a worst-case optimal join algorithm in C.}
\resumeItem{2023 -- \href{https://github.com/filippovisconti/mini-acme}{\underline{mini-acme}} -- Developed a minimal ACME client in Python.}
\resumeItem{2022 -- \href{https://github.com/filippovisconti/Fuzzible}{\underline{Fuzzible}} -- Developed a fuzzing tool for Ansible modules using Python and Docker containers.}
\resumeItem{2021 -- \href{https://github.com/filippovisconti/mcproject}{\underline{FillYourTeam!}}  -- Developed a multi-platform app using Xamarin framework and MVVM architecture.}
% \resumeItem{Mentored and collaborated with 2 team members.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Ecotherm S.p.A.}{Rome (Italy)}
{Freelance Software Developer}{Dec 2023}
\resumeItemListStart
\resumeItem{Migrated an internal web GIS application from a legacy LAMP stack to a modern one.}
\resumeItem{Fixed bugs and added new features.}
\resumeItem{Installed and setup a new dedicated server.}
\resumeItemListEnd

\resumeSubheading
{Bytewise S.r.l.}{Rome (Italy)}
{System Engineering Intern}{Mar 2022 -- June 2022}
\resumeItemListStart
\resumeItem{Designed and installed a cyber defense system for a small business, including assembling the hardware.}
\resumeItem{Installed and configured servers, for services like firewall, proxy, reverse proxy, DNS, DHCP, VPN, IDS, IPS.}
\resumeItem{Installed and managed routers and switches, configured VLANS, site-to-site WireGuard VPNs.}
\resumeItem{Worked on RHEL and Debian-based ditributions.}
\resumeItem{Performed basic penetration testing using nmap, Metasploit, OpenVAS, dirbuster, and others.}
\resumeItemListEnd

\resumeSubheading
{CyberChallenge.it}{Rome (Italy)}
{Participant}{\textit{Feb 2023 -- June 2023}}
\resumeItemListStart
\resumeItem{Participated in the 2023 edition of the CyberChallenge.it, a national cybersecurity competition.}
\resumeItem{Ranked 1st in the local competition.}
\resumeItem{Ranked 26th over 41 in the national competition.}
\resumeItemListEnd

\resumeSubheading
{Talks}{}
{Seminar speaker at Università degli Studi Roma TRE}{}
\resumeItemListStart
\resumeItem{Intro to Hardware Vulnerabilities (Rowhammer, Meltdown) - Rome, January 2024}
\resumeItem{Intro to Stack Overflows and Buffer Overflows -  Rome, March 2023}
\resumeItemListEnd


\resumeSubHeadingListEnd




%-----------PROJECTS-----------
\section{Other Experiences}
\resumeSubHeadingListStart

\resumeSubheading
{Università degli Studi Roma TRE}{Rome (Italy)}
{ICT Support and Management}{Mar 2021 -- June 2022}
\resumeItemListStart
\resumeItem{Managed accounts and software licenses.}
\resumeItem{Provided support through a technical helpdesk.}
\resumeItemListEnd

\resumeSubheading
{Head of the Model International Court of Justice}{Rome (Italy)}
{Liceo Scientifico Statale Farnesina}{Sept 2019 -- Feb 2020}
\resumeItemListStart
\resumeItem{Organized and managed the sessions for the Model International Court of Justice.}
\resumeItemListEnd


\resumeSubheading
{Delegate at the Model United Nations}{San Jose (California, USA)}
{Santa Teresa High School}{Jan 2019}
\resumeItemListStart
\resumeItem{Participated in the Model United Nations conference, as a country representative in the Legal Committee.}
    \resumeItemListEnd

\resumeSubHeadingListEnd
%
%----------- SKILLS-----------
\section{Languages, Skills and Interests}
\begin{itemize}[leftmargin=0.15in, label={}]
	\small{\item{
	      \textbf{Languages}{: Italian: mother tongue. English: excellent (C2). Spanish: fair.} \\
          \textbf{Licences}{: A2 motorcycle, B car, Unrestricted Boating licence (both sailing and motor), Drone Open A1-A3 licence.}
	      \textbf{Hobbies}{: music production, sailing, motorcycles, restoring classic cars.}
	      }}
\end{itemize}

%-----------PROJECTS-----------------
%\section{Projects}
% \resumeSubHeadingListStart
%  \resumeSubItem{QuantSoftware Toolkit}
%   {Open source python library for financial data analysis and machine learning for finance.}
%\resumeSubItem{Github Visualization}
% {Data Visualization of Git Log data using D3 to analyze project trends over time.}
%\resumeSubItem{Recommendation System}
% {Music and Movie recommender systems using collaborative filtering on public datasets.}
%\resumeSubItem{Mac Setup}
% {Book that gives step by step instructions on setting up developer environment on Mac OS.}
%\resumeSubHeadingListEnd



%-------------------------------------------
\end{document}
